---
name: "Climate_Azerbaijan"
title: "Climatic Trends in Azerbaijan"
subtitle: <h2>IAMO Leibniz Institute of Agricultural Development in Transition Economies, Max Hofmann, 29.07.2021</h2>
output:
  html_document:
    theme: united
    toc: true
    df_print: kable
    number_sections: false
    toc_depth: 3
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
<style>
  h1.title{
    font-size: 38px !important;
    color: black !important;
  }
  h1{
    font-size: 30px !important;
    color: #dd4814 !important;
  }
  h2{
    font-size: 25px !important;
    color: #808080 !important;
  }
  h3{
    font-size: 20px !important;
    color: #404040 !important;
  }
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


&nbsp;


***


<!-- ## PREPARATIONS -->
```{r, warning=FALSE, message=FALSE, echo=FALSE}
## load packages
library(leaflet)
library(leaflet.extras)
library(magrittr)
library(raster)
library(rgdal)
library(sp)
library(dplyr)
library(stringr)
library(mapview)

## define root directory
drive <- "X:"

colred <- colorRampPalette(rev(c("#B2182B","#D6604D","#F4A582","#FDDBC7")))
colramp_red <- colred(100)
```

<!-- ## LOAD AND PRE-PROCESS ADMINISTRATIVE DIVISIONS DATA -->
```{r, warning=FALSE, message=FALSE, echo=FALSE}
## load auxiliary file (we need the coordinate system of this one for correct visualization in leaflet)
US3 <- readOGR("X:/PROJECTS/Sparkassenstiftung/data_work/WP_2.1/inputs/election_counties/2004_Election_Counties.shp", verbose=FALSE)
```

<!-- ## TEST IMPORT -->
```{r, warning=FALSE, message=FALSE, echo=FALSE}
# arm_prcp_adm01 <- readOGR("X:/PROJECTS/Sparkassenstiftung/data_work/WP_2.1/outputs/Trends_Shapefiles_growingseason/ARM_PRCP_Admin01_1981_2020.shp", verbose=FALSE)
# arm_prcp_adm02 <- readOGR("X:/PROJECTS/Sparkassenstiftung/data_work/WP_2.1/outputs/Trends_Shapefiles_growingseason/ARM_PRCP_Admin02_1981_2020.shp", verbose=FALSE)
# arm_prcp_koepp <- readOGR("X:/PROJECTS/Sparkassenstiftung/data_work/WP_2.1/outputs/Trends_Shapefiles_growingseason/ARM_PRCP_KoeppenPresent_1981_2020.shp", verbose=FALSE)
# 
# aze_prcp_adm01 <- readOGR("X:/PROJECTS/Sparkassenstiftung/data_work/WP_2.1/outputs/Trends_Shapefiles_growingseason/AZE_PRCP_Admin01_1981_2020.shp", verbose=FALSE)
# aze_prcp_adm02 <- readOGR("X:/PROJECTS/Sparkassenstiftung/data_work/WP_2.1/outputs/Trends_Shapefiles_growingseason/AZE_PRCP_Admin02_1981_2020.shp", verbose=FALSE)
# aze_prcp_koepp <- readOGR("X:/PROJECTS/Sparkassenstiftung/data_work/WP_2.1/outputs/Trends_Shapefiles_growingseason/AZE_PRCP_KoeppenPresent_1981_2020.shp", verbose=FALSE)
# 
# head(arm_prcp_adm01@data)
# head(arm_prcp_adm02@data)
# head(arm_prcp_koepp@data)
# 
# head(aze_prcp_adm01@data)
# head(aze_prcp_adm02@data)
# head(aze_prcp_koepp@data)
```


<!-- ## PLOT FUNCTION -->
```{r, warning=FALSE, message=FALSE, echo=FALSE} 
plot_trends <- function(tempscale, temp_string, country, para, zones, para_full) {
  
  if (tempscale == 0) { 
    dir_temp <- "X:/PROJECTS/Sparkassenstiftung/data_work/WP_2.1/outputs/Trends_Shapefiles_growingseason/"
    endyear <- 2019
  } else if (tempscale%in%c(1:12)) { 
    dir_temp <- "X:/PROJECTS/Sparkassenstiftung/data_work/WP_2.1/outputs/Trends_Shapefiles_monthly/" 
    endyear <- 2020 }

  if (para=="PRCP") {
    unit <- "mm"
    colredblue <- colorRampPalette(c("#B2182B","#D6604D","#F4A582","#FDDBC7","#F7F7F7","#D1E5F0","#92C5DE","#4393C3","#2166AC"))
    colramp <- colredblue(100)

  } else if (para%in%c("TAVG","TMIN","TMAX")) {
    unit <- "degrees Celsius"
    colredblue <- colorRampPalette(rev(c("#B2182B","#D6604D","#F4A582","#FDDBC7","#F7F7F7","#D1E5F0","#92C5DE","#4393C3","#2166AC")))
    colramp <- colredblue(100)
  }
  
  if (country=="ARM") {
    longi <- 44.93135
    lati <- 40.31175
  } else if (country=="AZE") {
    longi <- 47.2016
    lati <- 39.9355
  }
    
  dat <- readOGR(paste0(dir_temp,country,"_",para,"_",zones,"_1981_2020.shp"),verbose=F)
  names(dat) <- c("Name_Eng","GID_1","change","signif")
  dat <- spTransform(dat, crs(US3))
  
  if (tempscale%in%c(1:12)) { 
    allvalues <- c(dat@data[,2],dat@data[,4],dat@data[,6],dat@data[,8],dat@data[,10],dat@data[,12],
                   dat@data[,14],dat@data[,16],dat@data[,18],dat@data[,20],dat@data[,22],dat@data[,24])
  
    dat@data <- dat@data[,c(1,tempscale*2,tempscale*2+1)]
    names(dat@data)[c(2,3)] <- c("change","signif")
  } else { allvalues <- dat@data$change }

  dat$change <- round(dat$change,digits=2)
  
  dat@data$signif2 <- NA
  dat@data$direction <- NA
  for (i in 1:NROW(dat@data))
  { if (dat@data$signif[i] == 1) { dat@data$signif2[i] <- "significant change" 
  } else if (dat@data$signif[i] == 0) { dat@data$signif2[i] <- "no significant change" }
    
    if (dat@data$change[i] > 0) { dat@data$direction[i] <- paste0("Increase of ", dat@data$change[i], " ", unit)  
    } else if (dat@data$change[i] == 0) { dat@data$direction[i] <- paste0("No change in ", para_full)  
    } else if (dat@data$change[i] < 0) { dat@data$direction[i] <- paste0("Decrease of ", dat@data$change[i], " ", unit)  } }
  
  colkey <- max(abs(min(na.omit(allvalues))),abs(max(na.omit(allvalues))))
  bins <- c(seq(from=-colkey,to=colkey,by=(colkey*2)/10)[1:5]-0.01,0,0.001,seq(from=-colkey,to=colkey,by=(colkey*2)/10)[7:11]+0.01)
  pal <- colorBin(colramp, domain = dat$value, bins = bins)

  legendlabels <- paste(round(bins,digits=2),round(bins[-1],digits=2),sep=" - ")
  legendlabels[6] <- 0 

  if(length(unique(dat$signif))==1) {
    
    if (unique(dat$signif)==1) { 
        weight_index <- 2
        color_index <- "black"
    } else {
        weight_index <- 1
        color_index <- "white" }
    
    labels <- sprintf(
    paste0("<strong>%s</strong><br/>%s from 1981 to ", endyear, " <br/><i>%s</i>"),
    dat$Name_Eng, dat$direction, dat$signif2
    ) %>% lapply(htmltools::HTML)

    plot <- leaflet(options = leafletOptions(minZoom = 0, maxZoom = 14, worldCopyJump = F)) %>%
      setView(longi, lati, zoom = 7) %>%
      setMapWidgetStyle(list(background= "white")) %>%
  
    addPolygons(data=dat,
      fillColor = ~pal(change), weight = weight_index, opacity = 1, color = color_index, fillOpacity = 0.9, 
      highlight = highlightOptions(weight = 5, color = "#666", fillOpacity = 1, bringToFront = TRUE),
      label = labels,
      labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"), textsize = "15px", direction = "auto")) %>%
  
    addLegend(data=dat, pal = pal, values = ~change, opacity = 0.9, title = paste0("Change in <br>", para_full, "<br> in ", unit," <br> during ", temp_string, " <br> from 1981 to ", endyear), position = "bottomleft", labFormat = function(type, cuts, p) { paste0(legendlabels) } )
  }
 
  else {
    
  dat_signif <- dat[which(dat$signif==1),]
  dat_nonsignif <- dat[-which(dat$signif==1),]

  labels_signif <- sprintf(
    paste0("<strong>%s</strong><br/>%s from 1981 to ", endyear, " <br/><i>%s</i>"),
    dat_signif$Name_Eng, dat_signif$direction, dat_signif$signif2
  ) %>% lapply(htmltools::HTML)

  labels_nonsignif <- sprintf(
    paste0("<strong>%s</strong><br/>%s from 1981 to ", endyear, " <br/><i>%s</i>"),
    dat_nonsignif$Name_Eng, dat_nonsignif$direction, dat_nonsignif$signif2
  ) %>% lapply(htmltools::HTML)

  plot <- leaflet(options = leafletOptions(minZoom = 0, maxZoom = 14, worldCopyJump = F)) %>%
    setView(longi, lati, zoom = 7) %>%
    setMapWidgetStyle(list(background= "white")) %>%

  addPolygons(data=dat_nonsignif,
    fillColor = ~pal(change), weight = 1, opacity = 1, color = "white", fillOpacity = 0.9,
    highlight = highlightOptions(weight = 5, color = "#666", fillOpacity = 1, bringToFront = TRUE, sendToBack = TRUE),
    label = labels_nonsignif,
    labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"), textsize = "15px", direction = "auto")) %>%
  
  addPolygons(data=dat_signif,
    fillColor = ~pal(change), weight = 2, opacity = 1, color = "black", fillOpacity = 0.9, 
    highlight = highlightOptions(weight = 5, color = "#666", fillOpacity = 1, bringToFront = TRUE),
    label = labels_signif,
    labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"), textsize = "15px", direction = "auto")) %>%
  
  addLegend(data=dat, pal = pal, values = ~change, opacity = 0.9, title = paste0("Change in <br>", para_full, "<br> in ", unit," <br> during ", temp_string, " <br> from 1981 to ", endyear), position = "bottomleft", labFormat = function(type, cuts, p) { paste0(legendlabels) } )

  }
  
plot
}
```



# Climate Trends {.tabset .tabset-fade .tabset-pills}

## PRCP {.tabset .tabset-fade .tabset-pills}

### Growing Season (Oct - June)
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(0, "Growing Season", "AZE", "PRCP", "Admin02", "Precipitation")
```

### January
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(1, "January", "AZE", "PRCP", "Admin02", "Precipitation")
```

### February
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(2, "February", "AZE", "PRCP", "Admin02", "Precipitation")
```

### March
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(3, "March", "AZE", "PRCP", "Admin02", "Precipitation")
```

### April
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(4, "April", "AZE", "PRCP", "Admin02", "Precipitation")
```

### May
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(5, "May", "AZE", "PRCP", "Admin02", "Precipitation")
```

### June
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(6, "June", "AZE", "PRCP", "Admin02", "Precipitation")
```

### July
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(7, "July", "AZE", "PRCP", "Admin02", "Precipitation")
```

### August
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(8, "August", "AZE", "PRCP", "Admin02", "Precipitation")
```

### September
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(9, "September", "AZE", "PRCP", "Admin02", "Precipitation")
```

### October
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(10, "October", "AZE", "PRCP", "Admin02", "Precipitation")
```

### November
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(11, "November", "AZE", "PRCP", "Admin02", "Precipitation")
```

### December
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(12, "December", "AZE", "PRCP", "Admin02", "Precipitation")
```


## TMIN {.tabset .tabset-fade .tabset-pills}

### Growing Season (Oct - June)
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(0, "Growing Season", "AZE", "TMIN", "Admin02", "Minimum Temperature")
```

### January
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(1, "January", "AZE", "TMIN", "Admin02", "Minimum Temperature")
```

### February
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(2, "February", "AZE", "TMIN", "Admin02", "Minimum Temperature")
```

### March
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(3, "March", "AZE", "TMIN", "Admin02", "Minimum Temperature")
```

### April
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(4, "April", "AZE", "TMIN", "Admin02", "Minimum Temperature")
```

### May
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(5, "May", "AZE", "TMIN", "Admin02", "Minimum Temperature")
```

### June
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(6, "June", "AZE", "TMIN", "Admin02", "Minimum Temperature")
```

### July
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(7, "July", "AZE", "TMIN", "Admin02", "Minimum Temperature")
```

### August
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(8, "August", "AZE", "TMIN", "Admin02", "Minimum Temperature")
```

### September
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(9, "September", "AZE", "TMIN", "Admin02", "Minimum Temperature")
```

### October
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(10, "October", "AZE", "TMIN", "Admin02", "Minimum Temperature")
```

### November
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(11, "November", "AZE", "TMIN", "Admin02", "Minimum Temperature")
```

### December
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(12, "December", "AZE", "TMIN", "Admin02", "Minimum Temperature")
```


## TAVG {.tabset .tabset-fade .tabset-pills}

### Growing Season (Oct - June)
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(0, "Growing Season", "AZE", "TAVG", "Admin02", "Average Temperature")
```

### January
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(1, "January", "AZE", "TAVG", "Admin02", "Average Temperature")
```

### February
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(2, "February", "AZE", "TAVG", "Admin02", "Average Temperature")
```

### March
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(3, "March", "AZE", "TAVG", "Admin02", "Average Temperature")
```

### April
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(4, "April", "AZE", "TAVG", "Admin02", "Average Temperature")
```

### May
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(5, "May", "AZE", "TAVG", "Admin02", "Average Temperature")
```

### June
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(6, "June", "AZE", "TAVG", "Admin02", "Average Temperature")
```

### July
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(7, "July", "AZE", "TAVG", "Admin02", "Average Temperature")
```

### August
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(8, "August", "AZE", "TAVG", "Admin02", "Average Temperature")
```

### September
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(9, "September", "AZE", "TAVG", "Admin02", "Average Temperature")
```

### October
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(10, "October", "AZE", "TAVG", "Admin02", "Average Temperature")
```

### November
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(11, "November", "AZE", "TAVG", "Admin02", "Average Temperature")
```

### December
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(12, "December", "AZE", "TAVG", "Admin02", "Average Temperature")
```


## TMAX {.tabset .tabset-fade .tabset-pills}

### Growing Season (Oct - June)
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(0, "Growing Season", "AZE", "TMAX", "Admin02", "Maximum Temperature")
```

### January
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(1, "January", "AZE", "TMAX", "Admin02", "Maximum Temperature")
```

### February
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(2, "February", "AZE", "TMAX", "Admin02", "Maximum Temperature")
```

### March
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(3, "March", "AZE", "TMAX", "Admin02", "Maximum Temperature")
```

### April
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(4, "April", "AZE", "TMAX", "Admin02", "Maximum Temperature")
```

### May
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(5, "May", "AZE", "TMAX", "Admin02", "Maximum Temperature")
```

### June
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(6, "June", "AZE", "TMAX", "Admin02", "Maximum Temperature")
```

### July
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(7, "July", "AZE", "TMAX", "Admin02", "Maximum Temperature")
```

### August
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(8, "August", "AZE", "TMAX", "Admin02", "Maximum Temperature")
```

### September
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(9, "September", "AZE", "TMAX", "Admin02", "Maximum Temperature")
```

### October
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(10, "October", "AZE", "TMAX", "Admin02", "Maximum Temperature")
```

### November
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(11, "November", "AZE", "TMAX", "Admin02", "Maximum Temperature")
```

### December
```{r, warning=FALSE, message=FALSE, echo=FALSE}
plot_trends(12, "December", "AZE", "TMAX", "Admin02", "Maximum Temperature")
```





```{r, warning=FALSE, message=FALSE, echo=FALSE}
```

